### 2018-05-13 Manuscript/manuscript.Rmd
About to remove old material

@@

Assumptions:
\begin{itemize}
\item Ones borrowed directly from Freedman
\item All regressions have same design matrix and sample size. Do they all need to have same exposure of interest?
\item Residuals have mean 0
\item Independent observation
\end{itemize}

@@

>>>>

<!-------------------------- --------------------------------->
<!------------- SECTION: TO DO -------------->
<!-------------------------- --------------------------------->

\section{To do}

\begin{itemize}
\item Connect the last theorem with number of rejections
\end{itemize}

@@

Assumptions:
\begin{itemize}
\item Ones borrowed directly from Freedman
\item Covariates are mean-centered?
\item All regressions have same design matrix and sample size. Do they all need to have same exposure of interest?
\item Residuals have mean 0
\item Independent observation
\end{itemize}

@@

<!-------------------------- REGULARITY ASSUMPTION ---------------------------->
\begin{assump}
\label{regularity_assump}
As a regularity condition on the design matrix, assume that for some constant $k>0$:
\begin{align*}
N \cdot B'B &\xrightarrow[N \to \infty]{P} k \\
\Leftrightarrow N \sum_{n=1}^N [(X'X)^{-1}X']^2_{ij} &\xrightarrow[n \to \infty]{P} k
\end{align*}
\end{assump}

\begin{remark}
To provide intuition, consider the assumption in the context of simple linear regression \textcolor{red}{($p=2$)} with a mean-centered exposure of interest, $X_1$. Define $S_1 = \sum_{n=1}^N X_{n1}$ and $S_2 = \sum_{n=1}^N X_{n1}^2$. Then we have:
\begin{align*}
X'X &= \begin{bmatrix}
N & S_1 \\
S_1 & S_2 
\end{bmatrix}\\ \\
(X'X)^{-1} &= \frac{1}{N S_2 - S_1^2} \begin{bmatrix}
S_2 & -S_1 \\
-S_1 & N 
\end{bmatrix}\\ \\
(X'X)^{-1}X' &= \frac{1}{N S_2 - S_1^2} \begin{bmatrix}
S_2 - X_{11} S_1 & \dotsb & S_2 - X_{N1} S_1 \\
-S_1 + X_{11}N & \dotsb & -S_1 + X_{N1} N 
\end{bmatrix}\\
\end{align*}

The regularity condition concerns the term:
\begin{align*}
N \sum_{n=1}^N B_n^2 &= N \sum_{n=1}^N [(X'X)^{-1}X']^2_{n1} \\
&= \frac{1}{ N S_2^2 - 2 S_2 S_1^2 + \frac{1}{N} S_2} \sum_{n=1}^N \left( X_{n1} N - S_1 \right)^2 \\
&= \frac{1}{ N S_2^2 - 2 S_2 S_1^2 + \frac{1}{N} S_2} \sum_{n=1}^N \left( N^2 X_{n1}^2 - 2N X_{n1} S_1 + S_1^2 \right) \\
&= \frac{N^2 S_2 - 2N S_1^2 + NS_1^2 }{N S_2^2 - 2 S_2 S_1^2 + \frac{1}{N} S_2} \\
&= \frac{N^2 S_2 - NS_1^2 }{N S_2^2 - 2 S_2 S_1^2 + \frac{1}{N} S_2} \\
&= \frac{\frac{S_2}{N} - \frac{S_1^2}{N^2} }{ \frac{S_2^2}{N^2} - 2 \frac{S_2}{N} \frac{S_1^2}{N^2} + \frac{S_2}{N^2} } \tag{$\div N^3$} \\
&\xrightarrow[N \to \infty]{P} 1 / \sigma^2_1
\end{align*}
The last line follows because, by mean-centering, we have $S_1/N \xrightarrow[N \to \infty]{P} 0$ and $S_2/N \xrightarrow[N \to \infty]{P} \sigma^2_1$. Thus, for simple linear regression, Assumption \ref{regularity_assump} holds if $\sigma^2_1 > 0$. 
\end{remark}
